Blocking-resistant communication through high-value web services

### 2014-07-07 docs/meek.tex
Remember to ack Psiphon.
Revise decoy routing coverage.

Decoy routing~\cite{decoyrouting} is a technique that puts
proxies in the middle of network paths, rather than at the endpoints.
Realizations of the decoy routing idea include Telex~\cite{telex}
and Cirripede~\cite{cirripede}.
Decoy routing asks friendly ISPs to deploy special software on routers that lie
between censored users and uncensored Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by decoy routers, and not by the censor.
On receiving a tagged communication, the decoy router shunts it away from its apparent destination
and toward the censored destination requested by the client.
Our work is conceptually similar to decoy routing,
though the action happens at the application layer rather than the network layer.
Both systems use a piece of network infrastructure as a decoy to redirect certain flows:
in decoy routing it is an ISP router; for us it is the front domain.
Both tag flows in a way that is visible only to the decoy router:
in decoy routing a tag may be, for example, a hash embedded in the TLS client randomness;
for us it is the HTTP Host header, encrypted within an HTTPS stream.
Decoy routing generally requires the cooperation of large, centrally located
router operators,
whereas we only need to buy web application hosting.

@@

% \cite{ccs2012-decoys}
% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is not clear whether ISPs are
willing to act against censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

@@

We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
Special thanks go to the members of the tor-qa and tor-dev mailing lists
who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel

>>>>

Decoy routing~\cite{decoyrouting} is a technique that puts
proxies in the middle of network paths, rather than at the ends.
Realizations of decoy routing include Telex~\cite{telex}
and Cirripede~\cite{cirripede}.
In decoy routing, friendly ISPs deploy special \emph{decoy} routers that lie
on network paths between censored users and uncensored Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by decoy routers, and not by the censor.
On receiving a tagged communication, the decoy shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar to decoy routing;
think of domain fronting as decoy routing at the application layer.
In place of a decoy router, domain fronting has a CDN edge server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while domain fronting uses the HTTP Host header, encrypted within HTTPS.

Schuhard et~al.~\cite{ccs2012-decoys}
introduce the idea of a \emph{routing adversary} against decoy routing,
and show that the connectivity of the Internet enables
censors to force network users onto paths that do not include decoys.
Simulations by Houmansadr et~al.~\cite{nodirectionhome}
show that even though such alternate paths exist,
they are many times more costly to the censor,
especially when decoys are placed strategically.

@@

@@

We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
Special thanks go to the members of the tor-qa and tor-dev mailing lists
who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Rod Hynes and Michael Hull of Psiphon.
